Computing Entropies With Nested Sampling

### 2017-04-08 paper/ms.tex
More promising setup

>>>>

\subsection*{Continuous case}

Consider a probability density function $f(x)$, defined on the real
line. The probability contained in an interval
$[x_0, x_0 + L]$, which has length $L$, is
\begin{align}
\int_{x_0}^{x_0 + L} f(x) \, dx &= F(x_0 + L) - F(x_0)
\end{align}
where $F(x)$ is the cumulative distribution function (CDF).
This probability can be considered as a function of two variables,
$x_0$ and $L$, which I will denote by $Q(,)$:
\begin{align}
Q(x_0, L) &= F(x_0 + L) - F(x_0).
\end{align}
The contribution of such an interval to an entropy expression
is `minus $p\log p$', i.e.
\begin{align}
h(x_0, L) &= -Q(x_0, L) \log Q(x_0, L).
\end{align}

Consider the rate of change of $h$ as the interval is shifted to
the right, but with its width $L$ held constant:
\begin{align}
\frac{\partial h}{\partial x_0} &= - \frac{\partial}{\partial x_0}
  Q(x_0, L) \log Q(x_0, L)
\end{align}
